Motivation

### 2017-07-18 Reports/USAID.Rmd
Creo oos plots para el ScaleUp, separo oos plots para Pilot

---
title: "Motivation"
output: 
  pdf_document: 
    keep_tex: yes
---

@@

@@

# First Pilot 
## Data
The data for the calculator developed for the pilot came from a sample of 1000 concluded case files from a single subcourt (subcourt 7). Defendants in subcourt 7 consist mostly of firms in XXX industries, so we were careful in correctly labeling casefiles containing at least one outsourcing firm within the list of defendants.

## Models
### Our questions

We aimed to provide three pieces of information:

@@

### Training and Evaluation

@@

#### Probability of outcomes

@@

For our classification problem, the dependent variable -a categorical variable depicting the case ending- was recoded into 5 dummy variables. The following models were then tested for classification of each binary outcome:

@@

**XXX (1) **
** Propuestas:** 
**A. Poner unos histogramas de accuracy rate entre modelos **
**B. Poner unas tablitas de la métrica en cuestión (i.e. accuracy rate y MAPD) **

#### Prediction models

@@

**XXX (2) **
** Propuestas:** 
**A. Poner unas scatter plots de y vs. ygorro como las que hice para el paper. **
**B. Poner unas tablitas de la métrica en cuestión (i.e. accuracy rate y MAPD)**

## Information

@@

# Scale-Up
## Data

@@

### Our Questions

3. Given a case ending in settlement, what would be the expected compensation?

### Training and Evaluation
#### Probability of winning

@@

#### Expected compensations

@@

## Information

>>>>

---
title: " "
output: 
  pdf_document: 
    keep_tex: yes
  number_sections: true
---

@@

# Motivation

@@

# First Pilot 
## Our questions
We aimed to provide three pieces of information:

@@

## Data
The data for our first calculator came from a sample of 1000 concluded case files from a single subcourt (subcourt 7). Defendants in subcourt 7 consist mostly of outsourcing, transportation firms and gas stations.

@@

### Discrete outcomes

@@

The dependent variable -a categorical variable depicting the case ending- was recoded into 5 dummy variables. The following models were then tested for classification of each binary outcome:

@@

XXX

### Continuous outcomes

@@

XXXXX

## Display of Information

@@

# Scale-Up
## Our Questions

3. Given a case ending in settlement, what would be the expected compensation?
## Data

@@

### Discrete outcomes

@@

### Continuous outcomes

@@

## Display of Information

### 2017-07-18 Reports/USAID.tex
Creo oos plots para el ScaleUp, separo oos plots para Pilot

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Motivation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Motivation}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\begin{document}
\maketitle

@@

The data for the calculator developed for the pilot came from a sample
of 1000 concluded case files from a single subcourt (subcourt 7).
Defendants in subcourt 7 consist mostly of firms in XXX industries, so
we were careful in correctly labeling casefiles containing at least one
outsourcing firm within the list of defendants.

\subsubsection{Our questions}\label{our-questions}

@@

\subsubsection{Training and Evaluation}\label{training-and-evaluation}

@@

\paragraph{Probability of outcomes}\label{probability-of-outcomes}

@@

\textbf{XXX (1) } ** Propuestas:** \textbf{A. Poner unos histogramas de
accuracy rate entre modelos } \textbf{B. Poner unas tablitas de la
métrica en cuestión (i.e.~accuracy rate y MAPD) }

\paragraph{Prediction models}\label{prediction-models}

@@

\textbf{XXX (2) } ** Propuestas:** \textbf{A. Poner unas scatter plots
de y vs.~ygorro como las que hice para el paper. } \textbf{B. Poner unas
tablitas de la métrica en cuestión (i.e.~accuracy rate y MAPD)}

\subsection{Information}\label{information}

@@

\subsection{Data}\label{data-1}

@@

\subsubsection{Our Questions}\label{our-questions-1}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Given a case ending in a court ruling, how likely is to recover a
  positive compensation?
\item
  What would be that expected compensation?
\item
  Given a case ending in settlement, what would be the expected
  compensation?
\end{enumerate}

\subsubsection{Training and Evaluation}\label{training-and-evaluation-1}

\paragraph{Probability of winning}\label{probability-of-winning}

@@

\paragraph{Expected compensations}\label{expected-compensations}

@@

\subsection{Information}\label{information-1}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{}
  \pretitle{\vspace{\droptitle}}
  \posttitle{}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\begin{document}

\section{Motivation}\label{motivation}

@@

\subsection{Our questions}\label{our-questions}

@@

The data for our first calculator came from a sample of 1000 concluded
case files from a single subcourt (subcourt 7). Defendants in subcourt 7
consist mostly of outsourcing, transportation firms and gas stations.

@@

\subsubsection{Discrete outcomes}\label{discrete-outcomes}

@@

XXX

\subsubsection{Continuous outcomes}\label{continuous-outcomes}

@@

XXXXX

\subsection{Display of Information}\label{display-of-information}

@@

\subsection{Our Questions}\label{our-questions-1}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Given a case ending in a court ruling, how likely is to recover a
  positive compensation?
\item
  What would be that expected compensation?
\item
  Given a case ending in settlement, what would be the expected
  compensation? \#\# Data
\end{enumerate}

@@

\subsubsection{Discrete outcomes}\label{discrete-outcomes-1}

@@

\subsubsection{Continuous outcomes}\label{continuous-outcomes-1}

@@

\subsection{Display of Information}\label{display-of-information-1}
